The reference model approach in feature selection problems \vspace{.1in}

### 2019-07-16 paper/ref_approach.tex
one more edit to section 2

\cite{paper:bodyfat} report results using steplm with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model. Here, we implement steplm via AIC without fixing any variable. For selection via projpred, the reference model includes all the covariates, we regularize model complexity with a regularised horseshoe prior on the covariate coefficients (cite), submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}. The experiments are implemented in \texttt{R} (cite). The steplm approach is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projpred is done with the \texttt{projpred} package. In order to automatise the latter, we select the submodel as the one with the smallest size which has an elpd score higher than the reference model score with probability 0.05. The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}. The projpred approach has only two variables, 'abdomen' and 'weight', with inclusion frequencies above 50\% ('abdomen' is the only included always), the third most included is `wrist' at 44\%, and the fourth is `height' at 35\%, while steplm has seven features above 50\%. Such a lower stability of steplm can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}. For exaple, the first five selected models have a cumulative frequency of 76\% with projpred, but only of 14\% with steplm. In addition, we note that the size of the selected model is much smaller when using projpred.

>>>>

\cite{paper:bodyfat} report results using steplm with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model. Here, we implement steplm via AIC without fixing any variable. For selection via projpred, the reference model includes all the covariates, we regularize model complexity with a regularised horseshoe prior on the covariate coefficients (cite), submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}. The experiments are implemented in \texttt{R} (cite). The steplm approach is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projpred is done with the \texttt{projpred} package. In order to automatise the latter, we select the submodel as the one with the smallest size which has an elpd score higher (i.e., better) than the reference model score with probability of at least 5\%. The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}. The projpred approach has only two variables, 'abdomen' and 'weight', with inclusion frequencies above 50\% ('abdomen' is the only included always), the third most included is `wrist' at 44\%, and the fourth is `height' at 35\%, while steplm has seven features above 50\%. Such a lower stability of steplm can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}. For exaple, the first five selected models have a cumulative frequency of 76\% with projpred, but only of 14\% with steplm. In addition, we note that the size of the selected model is much smaller when using projpred.
